### 2021-02-26 tex/imp.tex
Clarify the last equation
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

    For choosing the value of $\alpha$ we can consider the number of time steps that the trust value of a user needs
    for reaching a specified fraction of his account balance.
    We know that for large $n$ and $|x| < 1$ we have $(1 + x)^{n} \approx e^{nx}$, so by letting $k = 0$ and $t = n$
    we can write:
    \[
        \alpha =- \frac{\ln\left(1 - \frac{M_{n}}{X}\right)}{n}
    \]
    The value of $\alpha$ for a desired configuration can be calculated by this equation.
    For instance, we could calculate the $\alpha$ for a relatively good configuration in which $M_{n} = 0.8X$ and $n$
    equals to the number of time steps of 10 years.
\end{document}

>>>>

    For choosing the value of $\alpha$ we can consider the number of time steps that the trust value of a user needs
    for reaching a specified fraction of his account balance.
    We know that for large $n$ and $|x| < 1$ we have $(1 + x)^{n} \approx e^{nx}$, so by letting $M_{k} = 0$ and
    $n = t - k$
    we can write:
    \[
        \alpha =- \frac{\ln\left(1 - \frac{M_{n + k}}{X}\right)}{n}
    \]
    The value of $\alpha$ for a desired configuration can be calculated by this equation.
    For instance, we could calculate the $\alpha$ for a relatively good configuration in which $M_{n+k} = 0.8X$ and $n$
    equals to the number of time steps of 10 years.
\end{document}
